Many claims of group polarization are plausibly false due to inappropriate statistics

### 2024-01-18 GroupPolarizationStatmod/paper/ms.tex
starting analyses writing and cleaning up model setup

\begin{figure}
  \caption{Group polarization is experimentally induced by first gathering
  participant responses to an opinion prompt (A). Then groups of like-minded 
  individuals discuss the prompt (B). Group 
  polarization occurs if the mean post-discussion opinion is more extreme 
  than the mean pre-discussion opinion (C).}
  \label{fig:groupPolarizationSchematic}
  \centering
  \includegraphics[width=\textwidth]{Figures/GPExperimentSketch.pdf}
\end{figure}

\spacing{1.0}
\input{tables/conditions_table.tex}
\spacing{1.5}

@@

\subsection{Metric linear models fail to identify simple consensus}

\spacing{1.0}
\hspace{-1em}
\input{t-test-table.tex}
% \input{t-test-table-custom.tex}
\spacing{1.5}

@@

>>>>

\begin{figure}
  \caption{Group polarization experiments trials in the ten studies
    analyzed here proceed in three steps: 
    (A) \textbf{Pre-deliberation.} Participant opinions are measured using an 
    ordinal scale. 
    (B) \textbf{Deliberation.} Groups discuss their opinions on the prompt. 
    (C) \textbf{Post-deliberation.} Participant opinions are measured again.
    Group polarization in one trial is said to occur if 
    the mean post-deliberation opinion is greater than the pre-deliberation 
    opinion.
}
  \label{fig:groupPolarizationSchematic}
  \centering
  \includegraphics[width=\textwidth]{Figures/GPExperimentSketch.pdf}
\end{figure}

% \spacing{1.0}
% \input{tables/conditions_table.tex}
% \spacing{1.5}

@@

\subsection{Metric linear models often fail to identify simple consensus}

Here we evaluate if metric linear models inferred group polarization from
simulated simple consensus data using parameters identified above. Those
parameters specified continous pre- and post-deliberation

% \spacing{1.0}
% \hspace{-1em}
% \input{t-test-table.tex}
% % \input{t-test-table-custom.tex}
% \spacing{1.5}

@@

  \mt{Idea: increase $N$ for simulations and see effect on distribution of Cohen's $d$
  for both metric and ordinal models}
